\Title

### 2023-02-20 Grimaldi-etal-BiolCybernetics.tex
Update on Overleaf.

By pruning weights, we observe that the evolution of accuracy as a function of the log percentage of active weights fits well a sigmoid curve. Half-saturation level is reached at about $3.5\times 10^{-3}\%$ of active weights, corresponding in our setting to a total amount of $6$ computations per decision. Compared to the full kernels, the accuracy of our method is maintained to its top performances when dividing the number of computations by a factor up to about $200$. In this case, the number of computations is greatly reduced compared to~\citep{grimaldi_robust_2022}, thus demonstrating the efficiency of the presented method. 
%
%%%-----------------------------------------------------------------
%: fig:accuracy
%%%-----------------------------------------------------------------
\begin{figure}%[h!]
    \centering
    \includegraphics[width=0.95\linewidth]{figures/quant_accuracy.pdf}
    \caption{Accuracy as a function of the number of computation load for the HD-SNN model (blue dots) with errorbars giving the 5\% - 95\% quantiles  and a sigmoid fit (blue line). The relative computational load (on a log axis) is controlled by changing the percentage of nonzero weights relative to the dense convolution kernel. As we prune coefficients, we observe a stable accuracy value, with a drop observed with approximately 25 times less computations.}
    \label{fig:accuracy}
\end{figure}
%
\section{Discussion}
%%%-----------------------------------------------------------------
In this paper, we have introduced a generic SNN with heterogeneous delays and shown how it compares favorably to a state-of-the-art event-based classification algorithm for a visual motion detection task. The learned model shares a number of similarities with neurobiological anatomical observations, as well as with behavioral results. The event-based computations of our method can be drastically reduced by pruning synapses, while maintaining top classification performance. This shows that we can take advantage of the precise timing of spikes to improve the performance of neural computations.
%
\subsection{Synthesis and main contributions}
%%%-----------------------------------------------------------------
The HD-SNN model that has been trained and evaluated on a complex motion detection task. The model has been defined to provide optimal detection of event-driven spatio-temporal motifs. We have shown that the model, when trained on a dataset of natural images with realistic eye movements, learns kernels similar to those found in the early visual cortex~\cite{kremkow_push-pull_2016}. %We then demonstrated that the model shows similarities to biological responses.
We have evaluated the computational cost of this model when implemented in a setting similar to event-based hardware. We show that the use of heterogeneous delays may be an efficient computational solution for future neuromorphic hardware, but also a key to understanding why spikes are a universal component of neural information processing.

>>>>

By pruning weights, we observe that the evolution of accuracy as a function of the log percentage of active weights fits well a sigmoid curve. Half-saturation level is reached at about $3.5\times 10^{-3}\%$ of active weights, corresponding in our setting to a total amount of $6$ computations per decision. Compared to the full kernels, the accuracy of our method is maintained to its top performances when dividing the number of computations by a factor up to about $200$. In this case, the number of computations is greatly reduced compared to~\citep{grimaldi_robust_2022}, thus demonstrating the efficiency of the presented method. 
%
%%%-----------------------------------------------------------------
%: fig:accuracy
%%%-----------------------------------------------------------------
\begin{figure}%[h!]
    \centering
    \includegraphics[width=0.95\linewidth]{figures/quant_accuracy.pdf}
    \caption{Accuracy as a function of computational load for the HD-SNN model (blue dots) with error bars indicating the 5\% - 95\% quantiles and a sigmoid fit (blue line). The relative computational load (on a logarithmic axis) is controlled by changing the percentage of nonzero weights relative to the dense convolution kernel. As we prune the coefficients, we observe a stable accuracy value, with a drop observed at about 25 times fewer computations.}
    \label{fig:accuracy}
\end{figure}
%
\section{Discussion}
%%%-----------------------------------------------------------------
In this paper, we have introduced a generic SNN with heterogeneous delays and shown how it compares favorably to a state-of-the-art event-based classification algorithm for a visual motion detection task. The learned model shares a number of similarities with neurobiological anatomical observations, as well as with behavioral results. The event-based computations of our method can be drastically reduced by pruning synapses, while maintaining top classification performance. This shows that we can take advantage of the precise timing of spikes to improve the performance of neural computations.
%
\subsection{Synthesis and main contributions}
%%%-----------------------------------------------------------------
The HD-SNN model that has been trained and evaluated on a complex motion detection task. The model has been defined to provide optimal detection of event-driven spatio-temporal motifs. We have shown that the model, when trained on a dataset of natural images with realistic eye movements, learns kernels similar to those found in the early visual cortex~\cite{kremkow_push-pull_2016}. %We then demonstrated that the model shows similarities to biological responses.
We have evaluated the computational cost of this model when implemented in a setting similar to event-based hardware. We show that the use of heterogeneous delays may be an efficient computational solution for future neuromorphic hardware, but also a key to understanding why spikes are a universal component of neural information processing.
